Arc Blanc: a real time ocean simulation framework

### 2024-11-14 paper.tex
fix redundancy
fix elusion

This expression depends on the ratio $r_{\omega}=\omega/\omega_p$ of $\omega$ and $\omega_p$, the latter being the same as in JONSWAP spectrum.
Hence, in \framework $\beta_s$ is defined as a mix of Donelan \etal (1985) \cite{donelanDirectionalSpectraWindgenerated1985} for $r_{\omega}<1.6$, and Banner (1990) \cite{bannerEquilibriumSpectraWind1990} for $r_{\omega}\geq1.6$.
Moreover, the case $r_{\omega}<0.56$ is removed, as suggested by C. Horvath.
Altogether, this leads to the following expression of $\beta_s$:
\begin{equation}
	\begin{aligned}
		 & \beta_s= \begin{cases}%
			            2.61\left(r_{\omega}\right)^{1.3}  & \text{for } r_{\omega}<0.95          \\
			            2.28\left(r_{\omega}\right)^{-1.3} & \text{for } 0.95 \leq r_{\omega}<1.6 \\
			            10^\epsilon                        & \text{for }  r_{\omega}\geq1.6       %
		            \end{cases}
	\end{aligned}
\end{equation}
where
\begin{equation}
	\epsilon=0.8393 \exp \left(-0.567\ln\left(r_{\omega}^2\right)\right)-0.4.
\end{equation}
Any directional spectrum $D(\omega,\theta)$ must satisfy the normalization condition:
\begin{equation}
	\label{equa:normalization}
	\int_{-\pi}^\pi D(\omega,\theta)d\theta = 1
\end{equation}
Hence, $Q_{DB}(\omega)$ is a normalization factor to make $D_{DB}(\omega, \theta)$ respect the condition \ref{equa:normalization}:
\begin{equation}
	\begin{aligned}
		Q_{DB}(\omega) & = \frac{1}{\displaystyle\int_{-\pi}^\pi \frac{1}{2}\beta_s\left(\operatorname{sech}\left(\beta_s \theta\right)\right)^2 d\theta} = \frac{1}{\tanh\left(\beta_s\pi\right)}
	\end{aligned}
\end{equation}

@@

Note that we applied a first normalization factor $Q_{DB}$ to the simple Donelan Banner spectrum (Equation \ref{equa:ddb}) before calculating this second normalization factor $\widetilde{Q_{DB\xi}}(r_{\omega})$. In fact, if we simply approximate the full-spectrum normalization factor before applying it, we'll be faced with a normalization problem, because for small values of $r_{\omega}$, $Q_{DB\xi}(\omega)$ will be very low and therefore numerically difficult to normalize.

>>>>

This expression depends on the ratio $r_{\omega}=\omega/\omega_p$ of $\omega$ and $\omega_p$, the latter being the same as in JONSWAP spectrum.
Hence, in \framework $\beta_s$ is defined as a mix of Donelan \etal (1985) \cite{donelanDirectionalSpectraWindgenerated1985} for $r_{\omega}<1.6$, and Banner (1990) \cite{bannerEquilibriumSpectraWind1990} for $r_{\omega}\geq1.6$.
Moreover, the case $r_{\omega}<0.56$ is removed, as suggested by C. Horvath.
Altogether, this leads to the following expression of $\beta_s$:
\begin{equation}
	\begin{aligned}
		 & \beta_s= \begin{cases}%
			            2.61\left(r_{\omega}\right)^{1.3}  & \text{for } r_{\omega}<0.95          \\
			            2.28\left(r_{\omega}\right)^{-1.3} & \text{for } 0.95 \leq r_{\omega}<1.6 \\
			            10^\epsilon                        & \text{for }  r_{\omega}\geq1.6       %
		            \end{cases}
	\end{aligned}
\end{equation}
where
\begin{equation}
	\epsilon=0.8393 \exp \left(-0.567\ln\left(r_{\omega}^2\right)\right)-0.4.
\end{equation}
Any directional spectrum $D(\omega,\theta)$ must satisfy the normalization condition:
\begin{equation}
	\label{equa:normalization}
	\int_{-\pi}^\pi D(\omega,\theta)d\theta = 1
\end{equation}
Hence, $Q_{DB}(\omega)$ is a normalization factor to make $D_{DB}(\omega, \theta)$ respect condition \ref{equa:normalization}:
\begin{equation}
	\begin{aligned}
		Q_{DB}(\omega) & = \frac{1}{\displaystyle\int_{-\pi}^\pi \frac{1}{2}\beta_s\left(\operatorname{sech}\left(\beta_s \theta\right)\right)^2 d\theta} = \frac{1}{\tanh\left(\beta_s\pi\right)}
	\end{aligned}
\end{equation}

@@

Note that we applied a first normalization factor $Q_{DB}$ to the simple Donelan Banner spectrum (Equation \ref{equa:ddb}) before calculating this second normalization factor $\widetilde{Q_{DB\xi}}(r_{\omega})$. In fact, if we simply approximate the full-spectrum normalization factor before applying it, we will be faced with a normalization problem, because for small values of $r_{\omega}$, $Q_{DB\xi}(\omega)$ will be very low and therefore numerically difficult to normalize.
